outline!

### 2016-05-16 paper.tex
paper: intro and diagram updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[latin1]{inputenc}

@@

Cloud providers are increasingly reliant upon application-specific extensions
to distributed storage system such as Ceph as is shown in
Figure~\ref{fig:objclass-dev} by a marked increase in Ceph extensions used in
production.

The construction of extensions is not limited to core developers; the
development community has been receptive to contributions with the recent
inclusion by CERN developers of an extension for performing limited numeric
operations on object data~\cite{cls_numops}.

This trend is also not limited to Ceph. AWS Lambda, Redis Lua, Redis Modules,
KV-Drives, and Rhea, are all recent examples of storage systems embracing the
power of including application-specific semantics. While Ceph has not yet
reached the point of directly exposing these features to users, the recent
inclusion of a mechanism for dynamically defining extensions using
Lua~\cite{cls_lua} suggests that aspects of this may soon appear.

If the growth illustrated in Figure~\ref{fig:objclass-dev} continues, the
amount of low-level C++ will grow large. Unfortunately, much of
this code is written assuming a performance profile defined by a combination
of the hardware and software versions available at the time of development. As
Ceph development continues at a fast pace, the cost of adapting to changing
assumptions regarding performance will become significant.

@@

@@

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
Category & Specialization & Methods \\ \hline
\multirow{2}{*}{Locking} & Shared & \multirow{2}{*}{6} \\
                         & Exclusive & \\ \hline
\multirow{3}{*}{Logging} & Replica & 3 \\
                         & State & 4 \\
                         & Timestamped & 4 \\ \hline
GC & Reference Counting & 4 \\ \hline
\multirow{4}{*}{Metadata} & RBD & 37 \\
 & RGW & 27 \\
 & User & 5 \\
 & Version & 5 \\ \hline
\end{tabular}
\caption{A variety of RADOS object storage classes exist that expose reusable
interfaces to applications.}
\label{tab:objclass-cats}
\end{table}

@@

\begin{figure*}[!ht]
    \centering
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/librados-sweep/output.soft.reset.2hr.png}
        \caption{a}
        \label{fig:vanilla-io-diff}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/basic-cls-rand-read/output.read.60min.png}
        \caption{b}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
        \caption{c}
    \end{subfigure}\hfill
    \caption{Shown here are the graphs and such that demonstrate that the same
        physical design choices are not the same between differing version of
    Ceph even on the same hardware.}
\end{figure*}

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[latin1]{inputenc}

@@

Storage systems are increasingly providing features that take advantage of
application-specific knowledge to achieve optimizations and provide unique
services. However, this trend is leading to the creation of a large amount of
low-level software extensions that will be difficult to maintain as system
software and hardware evolve.

The widely deployed Ceph distributed storage system is an example of a storage
system that supports application-specific extensions in the form of custom I/O
interfaces to objects within the underlying RADOS object storage
system~\cite{weil:osdi06,weil:pdsw07}. Organizations are increasingly reliant
upon these extensions as is shown in Figure~\ref{fig:objclass-dev} by a marked
increase in the number of object operations that are packaged are part of the
Ceph distribution.  In addition to the growth of the quantity of operations,
Figure~\ref{fig:objclass-dev} also depicts the amount of low-level C++ written
to implement the set object operations. Unfortunately, this code is written
assuming a performance profile defined by the combination of the hardware and
software versions available at the time of development. As Ceph continues to
evolve at a fast pace, the cost of adapting application-specific codes to
changing assumptions regarding performance may become significant.

This trend is also not limited to Ceph. AWS Lambda, Redis Lua, Redis Modules,
KV-Drives, and Rhea, are all recent examples of storage systems embracing the
power of including application-specific semantics.

@@

And the construction of object operations is not limited to core Ceph
developers; the development community has been receptive to contributions with
the recent inclusion by CERN developers of an extension for performing limited
numeric operations on object data~\cite{cls_numops}, and all 
While Ceph has not yet
reached the point of directly exposing these features to users, the recent
inclusion of a mechanism for dynamically defining extensions using
Lua~\cite{cls_lua} suggests that aspects of this may soon appear.

@@

\begin{table}
\centering
\begin{tabularx}{\columnwidth}{|X|l|l|l|}
\hline
Category & Specialization & Methods \\ \hline
\multirow{2}{*}{Locking} & Shared & \multirow{2}{*}{6} \\
                         & Exclusive & \\ \hline
\multirow{3}{*}{Logging} & Replica & 3 \\
                         & State & 4 \\
                         & Timestamped & 4 \\ \hline
Garbage Collection & Ref. Counting & 4 \\ \hline
\multirow{4}{*}{Metadata} & RBD & 37 \\
 & RGW & 27 \\
 & User & 5 \\
 & Version & 5 \\ \hline
\end{tabularx}
\caption{A variety of RADOS object storage classes exist that expose reusable
interfaces to applications.}
\label{tab:objclass-cats}
\end{table}

@@

\begin{figure*}[!ht]
    \centering
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/librados-sweep/jewel_ssd.png}
        \caption{a}
        \label{fig:vanilla-io-diff}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/librados-sweep/firefly_ssd.png}
        \caption{b}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
        \caption{c}
    \end{subfigure}\hfill
    \caption{Shown here are the graphs and such that demonstrate that the same
        physical design choices are not the same between differing version of
    Ceph even on the same hardware.}
\end{figure*}
